\sysfull

### 2017-08-11 paper/paging.tex

\todo{Redo this figure to actually reflect paging -- right now it isn't clear if x,y,z are in a page or not, it isn't clear when the page gets copied to pagesTemp, it isn't clear what state we add to the system to help with commit, etc (i.e., dirty bits, commit bit).  Make this figure's labels consistent with the text: pagesTemp, RVAR, WVAR, explicit
commit in task, Page Buffer}{whoever}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{figures/sram-buffer}
	\caption{The interaction between the task, volatile buffer and the non-volatile memory (FRAM). Initially, the persistent variable \texttt{x} is not in the volatile buffer but \texttt{y} and \texttt{z} are.}
	\label{fig:volatile-buffer}
\end{figure}

>>>>

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.75\columnwidth]{figures/sram-buffer}
	\caption{The interaction between the task, volatile buffer and the non-volatile memory (FRAM). Initially, the persistent variable \texttt{x} is not in the volatile buffer but \texttt{y} and \texttt{z} are.}
	\label{fig:volatile-buffer}
\end{figure}
